TBA

### 2020-08-05 manuscript.tex
Updates from Overleaf

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{CJK}
\usepackage{framed}
\usepackage[hidelinks]{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}

@@

TEST CITE \cite{Phys2014}

\section{\label{sec:intro}Introduction}
Should be 4-5 paragraphs (funnel shaped) with similar structure to other papers in the field.

@@

@@

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/skeleton/microstate_optimization.png}
        \caption{Finding optimal amount of microstates for SRV and TICA clustering. VAMP-2 scores are consistently higher when clustering in SRV space}
        \label{fig:sample_fray}
	\end{center}
\end{figure}

@@

It is unclear the extent to which these interactions are physical given the strain required to form these shifted loops (need to discuss toehold loop experiments with Brennan).  Single shifted 3' and double shifted 5' strands have much lower population of these shifted loops (need to perform calculations to see if these account for increased stabilization of single shifted 5' versus single shifted 3'). Not sure how much more I should reall go into here...

@@

When examining these same four sequences using T-jump spectroscopy, Sandstead et al. found that the GC-core had the highest deviation from two-state behavior during dissociation \citep{Sanstead2016}. As their analysis did not consider the previously mentioned shifted states, this intermediate state was defined by a high degree of fraying about the central core. While high amounts of 1-2 base pair fraying were observed for GC-mid and AT-all as well, lattice model predictions that GC-core was the only sequence to have multiple frayed pairs during the dissociation process. Further analysis speculated that AT-all termini fraying was an effectively barrierless process characterized by rapid inter-conversion between all accessible frayed states \citep{Sanstead2018DirectDehybridization}. We see the same rapid fraying in simulation data (which too fast to be attributed with an SRV mode), however we stipulate that this inter-conversion first relies on the formation of the the AT-bond nearest to the GC center. In visualizing trajectories, we observe that the frayed ends rotate away from each other and impede helix formation, further highlighting the importance of this 4th base pair formation.

(free energy minimum at high temp but not low temp?).

\citep{Sanstead2018DirectDehybridization} Our data support a picture in which the dimer ensemble can exist in a broad basin where the populated configurations are not separated by appreciable barriers, suggesting rapid interconver- sion can occur between all of the accessible frayed structures within the well. GC-end placement leads to all or nothing mechanism.

@@

6K.-Y. Wong and B. M. Pettitt, “The pathway of oligomeric DNA melting investigated by molecular dynamics simulations,” Biophys. J. 95, 5618– 5626 (2008).
37A. Perez and M. Orozco, “Real-time atomistic description of DNA unfold- ing,” Angew. Chem. 49, 4805–4808 (2010).
38M. F. Hagan, A. R. Dinner, D. Chandler, and A. K. Chakraborty, “Atomistic understanding of kinetic pathways for single base-pair binding and unbind- ing

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/skeleton/tica_comparison_GC-core.PNG}
        \caption{SRV vs. TICA MSMs and resulting clsuter memberships}
        \label{fig:tica_comparison}
	\end{center}
\end{figure}

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/skeleton/all_modes_correlations.PNG}
        \caption{For Supplemental info: Correlations between all leading modes}
        \label{fig:all_modes}
	\end{center}
\end{figure}

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage{CJK}https://www.overleaf.com/project/5e820b28d741e00001b1ccac
\usepackage{framed}
\usepackage[hidelinks]{hyperref}
\usepackage{algorithm}
\usepackage{algpseudocode}
\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}

@@

\section{\label{sec:intro}Introduction}

@@

\subsection{\label{sec:methods}3spn2 Model}
Not sure if this is necessary, but can include a quick summary of model, why we chose to use it, and interesting features.
-Compatible with lammps
-Enough resolution to deserve dynamical behavior, coarse enough to run equlibrium sims
-Previous hybridization experiments show good agreement with experiments

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/srv_crossval.png}
        \caption{Cross val procedure to selection number of SRV coordinates (probably will be SI, but could include AT-all cross-val in the walkthrough section)}
        \label{fig:srv_crossval}
	\end{center}
\end{figure}

@@

@@

It is unclear the extent to which these interactions are physical given the strain required to form these shifted loops (need to discuss toehold loop experiments with Brennan).  Single shifted 3' and double shifted 5' strands have much lower population of these shifted loops (need to perform calculations to see if these account for increased stabilization of single shifted 5' versus single shifted 3'). Not sure how much more much to go into here ...

@@

When examining these same four sequences using T-jump and 2D spectroscopy, Sandstead et al. found that the GC-core had the highest deviation from two-state behavior during dissociation \citep{Sanstead2016}. As their analysis did not consider the previously mentioned shifted states, this intermediate state was defined by a high degree of fraying about the central core. While 1-2 base pair fraying was commonly observed for GC-mid and AT-all as well, lattice model predictions showed that GC-core had substantially more frayed base pairs. Further analysis showed that AT termini fraying was an effectively barrierless process characterized by rapid inter-conversion between all accessible frayed states \citep{Sanstead2018DirectDehybridization}. We see the same rapid fraying in simulation data (which too fast to be attributed with an SRV mode), however we stipulate that this inter-conversion first relies on the formation of the the AT-bond nearest to the GC center. In visualizing trajectories, we observe that the frayed ends rotate away from each other and impede helix formation, further highlighting the importance of this 4th base pair formation.

@@

6K.-Y. Wong and B. M. Pettitt, “The pathway of oligomeric DNA melting investigated by molecular dynamics simulations,” Biophys. J. 95, 5618– 5626 (2008).
37A. Perez and M. Orozco, “Real-time atomistic description of DNA unfold- ing,” Angew. Chem. 49, 4805–4808 (2010).
38M. F. Hagan, A. R. Dinner, D. Chandler, and A. K. Chakraborty, “Atomistic understanding of kinetic pathways for single base-pair binding and unbinding

@@

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/all_seq_tica_cvs.PNG}
        \caption{All sequences plotted on combined TICA axes}
        \label{fig:all_seq_tica_cvs}
	\end{center}
\end{figure}

\begin{figure}[ht!]
	\begin{center}
        \includegraphics[width=\textwidth]{Figs/figs_0804/all_seq_physical_cvs.PNG}
        \caption{All sequences and metastable macrostates plotted on frayed/shifted collective variable axes}
        \label{fig:all_seq_physical_cvs}
	\end{center}
\end{figure}

@@
